---
output: html_document
---
Examination of ODNB processing results
--------------------


```{r setup, include=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
source("code/ODNB/ODNB_setup.R")
ODNBID = 25200
## ODNB 18800 = Milton, 25200 = Shakespeare
```


## Table of contents {#toc}
- [Raw HTML file](#rawHtml)
- [Processed text file (accents removed, HTML cleaned up)](#rawplain)
- [Extracted Metadata](#metadata)
- [NER Tagging (after some aggregation)](#imptags)
- [Final biography matches](#finmatch)


## Raw HTML file (with empty lines stripped) {#rawHtml}
[Return to Table of Contents](#toc)
```{r loadhtml, echo=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_rawHTML)
rawHTML = ODNB_rawHTML[[ODNBID]]
s = rm_emptylines(rawHTML)
for(j in seq_along(s)) {cat("[*** Line",j,"***]", s[j], "\n")}
rm(ODNB_rawHTML)
```

## Processed text (right before NER) {#rawplain}
[Return to Table of Contents](#toc)
```{r loadplain, echo=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_splitcosub)
cat("This biography is of cosubject type '", ODNB_cosubstatus[ODNBID], "'\n\n", sep = "")

s = ODNB_cleantext[[ODNBID]]
for(j in seq_along(s)) {cat("[*** Paragraph",j,"***]", s[j], "\n")}

rm(ODNB_text, ODNB_cleantext)
```

## Metadata {#metadata}
[Return to Table of Contents](#toc)
```{r metadata, echo = FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_metadata)
trow = t(full_metadata[which(ODNBID == full_metadata$ID),])
rownames(trow) = NULL
colnames(trow) = NULL
print(cbind(colnames(full_metadata), trow))
```

## Combined NER information {#imptags}
[Return to Table of Contents](#toc)
```{r imptags, echo = FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_post_improvedpred)

cat("All names found in biography: \n")
print(ODNB_improvedpred[[ODNBID]][[1]])

cat("All matches in biography: \n")
print(ODNB_improvedpred[[ODNBID]][[2]])
rm(ODNB_improvedpred)
```

## Final Matches {#finmatch}
[Return to Table of Contents](#toc)
```{r finmatch, echo = FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_post_entitymatrix)
keep = which(big_entity_matrix$DocumentNum == ODNBID)
temp = big_entity_matrix[keep,]
rownames(temp) = NULL
temp$DocumentNum = NULL
print(temp)
```




