---
output: html_document
---
Examination of ODNB processing results
--------------------


```{r setup, include=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
source("code/ODNB/ODNB_setup.R")
ODNBID = 18800
```


## Table of contents {#toc}
- [Raw HTML file](#rawHtml)
- [Processed text file (accents removed, HTML cleaned up)](#rawplain)

## Raw HTML file (with empty lines stripped) {#rawHtml}

[Return to Table of Contents](#toc)
```{r loadhtml, echo=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_rawHTML)
rawHTML = ODNB_rawHTML[[ODNBID]]
s = rm_emptylines(rawHTML)
for(j in seq_along(s)) {cat("[*** Line",j,"***]", s[j], "\n")}
rm(ODNB_rawHTML)
```

## Processed text (right before NER) {#rawplain}
[Return to Table of Contents](#toc)
```{r loadplain, echo=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_splitcosub)
if (!is.null(ODNB_cleantext[[ODNBID + 100000]])) {
  cat("There is a cosubject listed with the same ODNBID; they were assigned an ODNB ID of", 
      ODNBID + 100000, ".\n")
}
s = ODNB_cleantext[[ODNBID[1]]]
for(j in seq_along(s)) {cat("[*** Paragraph",j,"***]", s[j], "\n")}

if (!is.null(ODNB_cleantext[[ODNBID + 100000]])) { 
  cat("Their section of the biography is given next.\n")
  ODNBID = c(ODNBID, ODNBID + 100000)
  s = ODNB_cleantext[[ODNBID[2]]]
  for(j in seq_along(s)) {cat("[*** Paragraph",j,"***]", s[j], "\n")}
}
## Do something about ODNBID + 100000. If this is the case, display & follow both users? OR do ODNBID mod 100000 in rawHTML. 
```



## This is the next section




## Load helper file scripts (to be replaced by SDFB library)
source("code/ODNB/text_processing/helper/clean_HTML_functions.R")
source("code/ODNB/text_processing/helper/NER_processing.R")
source("code/ODNB/text_processing/helper/NER_improve.R")

## Load the file location variables. 
source("code/ODNB/ODNB_file_locations.R")





