---
output: html_document
---
Examination of ODNB processing results
--------------------


```{r setup, include=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
source("code/ODNB/ODNB_setup.R")
ODNBID = 18800
```


## Table of contents {#toc}
- [Raw HTML file](#rawHtml)
- [Processed text file (accents removed, HTML cleaned up)](#rawplain)

## Raw HTML file (with empty lines stripped) {#rawHtml}

[Return to Table of Contents](#toc)
```{r loadhtml}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_rawHTML)
rawHTML = ODNB_rawHTML[[ODNBID]]
s = rm_emptylines(rawHTML)
for(j in seq_along(s)) {cat("[*** Line",j,"***]", s[j], "\n")}
rm(ODNB_rawHTML)
```

## Processed text (right before NER) {#rawplain}
[Return to Table of Contents](#toc)
```{r loadplain}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
#load(zzfile_textproc_preproc_splitcosub)
print('hello')
```



## This is the next section




## Load helper file scripts (to be replaced by SDFB library)
source("code/ODNB/text_processing/helper/clean_HTML_functions.R")
source("code/ODNB/text_processing/helper/NER_processing.R")
source("code/ODNB/text_processing/helper/NER_improve.R")

## Load the file location variables. 
source("code/ODNB/ODNB_file_locations.R")





