Examination of ODNB processing results
--------------------


```{r setup, include=FALSE}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
source("code/ODNB/ODNB_setup.R")
ODNBID = 18800
```

## Table of contents 
- Raw HTML file
- Processed text file (accents removed, HTML cleaned up)

[rawHtml]: #rawHtml
## Raw HTML file (with empty lines stripped)

```{r loadhtml}
setwd(gsub("sdfb_network.*", "sdfb_network", getwd()))
load(zzfile_textproc_preproc_rawHTML)
rawHTML = ODNB_raw[[ODNBID]]
s = rm_emptylines(rawHTML)
for(j in seq_along(s)) {cat("[*** Line",j,"***]", s[j], "\n")}
rm(ODNB_raw)
```

## Processed text (right before NER)

## This is the next section




## Load helper file scripts (to be replaced by SDFB library)
source("code/ODNB/text_processing/helper/clean_HTML_functions.R")
source("code/ODNB/text_processing/helper/NER_processing.R")
source("code/ODNB/text_processing/helper/NER_improve.R")

## Load the file location variables. 
source("code/ODNB/ODNB_file_locations.R")





